|

### 2023-01-28 paper.Rmd
Sat Jan 28 14:00:06 CET 2023: update-remote.sh

Since previous research on DAE-GP used a single hidden layers for the airfoil dataset [@dae-gp_2022_symreg], I repeated the experiment with a single hidden layer. Based on the findings of @pmlr-v5-erhan09a, I expected that pre-training DAE-GP would lead to a worsening

To confirm the research by @pmlr-v5-erhan09a

The experiments was repeated using the same setup with the only difference being a reduction from two hidden layers to 1 hidden layer.

![Best Fitness over 30 Generations - 1 hidden Layer - Airfoil](./img/airfoil_1hl_maxIndSize_fullRun_30gens/mean_median_fitness_byGens.png)

>>>>

Since previous research on DAE-GP used a single hidden layers for the airfoil dataset [@dae-gp_2022_symreg], I repeated the experiment with a single hidden layer. Based on the findings of @pmlr-v5-erhan09a, I expected that pre-training DAE-GP would lead to a decrease in overall performance. Figures \@ref(fig:airfoil-fitness-perGen) and \@ref(fig:airfoil-finalFitness) show the average best fitness per generation as well as the distribution of final fitness scores after 30 generations. The results are, again, based on $10$ individual runs per algorithm. As expected it shows, that for a small DAE-LSTM size pre-training negativley impacts the fitness of solution found by DAE-GG.

```{r airfoil-fitness-perGen, echo=FALSE, fig.cap="Fitness over 30 Generations - Airfoil (1HL)", out.width="80%"}
knitr::include_graphics("./img/airfoil_1hl_maxIndSize_fullRun_30gens/mean_median_fitness_byGens.png")
```

```{r airfoil-finalFitness, echo=FALSE, fig.cap="Fitness after 30 Generations - Airfoil (1HL)", out.width="80%"}
knitr::include_graphics("./img/airfoil_1hl_maxIndSize_fullRun_30gens/final_fit_boxplot.png")
```

### 2023-01-28 paper.tex
Sat Jan 28 14:00:06 CET 2023: update-remote.sh

\hypertarget{airfoil-dateset---2-hidden-layers}{%
\subsubsection{Airfoil Dateset - 2 hidden Layers}\label{airfoil-dateset---2-hidden-layers}}

@@

The experiments was repeated using the same setup with the only difference being a reduction from two hidden layers to 1 hidden layer.

\begin{figure}
\centering
\includegraphics{./img/airfoil_1hl_maxIndSize_fullRun_30gens/mean_median_fitness_byGens.png}
\caption{Best Fitness over 30 Generations - 1 hidden Layer - Airfoil}
\end{figure}

>>>>

\hypertarget{airfoil-dataset---2-hidden-layers}{%
\subsubsection{Airfoil Dataset - 2 Hidden Layers}\label{airfoil-dataset---2-hidden-layers}}

@@

\hypertarget{airfoil-dataset---1-hidden-layer}{%
\subsubsection{Airfoil Dataset - 1 Hidden Layer}\label{airfoil-dataset---1-hidden-layer}}

Since previous research on DAE-GP used a single hidden layers for the airfoil dataset {[}\protect\hyperlink{ref-dae-gp_2022_symreg}{17}{]}, I repeated the experiment with a single hidden layer. Based on the findings of {[}\protect\hyperlink{ref-pmlr-v5-erhan09a}{3}{]}, I expected that pre-training DAE-GP would lead to a decrease in overall performance. Figures \ref{fig:airfoil-fitness-perGen} and \ref{fig:airfoil-finalFitness} show the average best fitness per generation as well as the distribution of final fitness scores after 30 generations. The results are, again, based on \(10\) individual runs per algorithm. As expected it shows, that for a small DAE-LSTM size pre-training negativley impacts the fitness of solution found by DAE-GG.

{\centering \includegraphics[width=0.8\linewidth]{./img/airfoil_1hl_maxIndSize_fullRun_30gens/mean_median_fitness_byGens}

\caption{Fitness over 30 Generations - Airfoil (1HL)}\label{fig:airfoil-fitness-perGen}
\end{figure}

{\centering \includegraphics[width=0.8\linewidth]{./img/airfoil_1hl_maxIndSize_fullRun_30gens/final_fit_boxplot}

\caption{Fitness after 30 Generations - Airfoil (1HL)}\label{fig:airfoil-finalFitness}
\end{figure}
